---
title: ""
output: github_document
---


```{r, eval=T, echo=F}
source('../inst/forelesningsnotater/timeplan.R')

```

## Introduksjon

Forelesning #1: [`r tema[1]`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/pdfs/1-3_introduksjon.pdf)

## Produsentteori: Produsentens økonomiske adferd

Forelesning #2: [`r tema[2]`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/pdfs/4_produsent_teknologi.pdf)

Forelesning #3: [`r tema[3]`](https://github.com/joernih/sfb10816mikrooekonomi/blob/main/inst/forelesningsnotater/pdfs/5_produsent_innt_kostn.pdf)

Forelesning #4: [`r tema[4]`](https://github.com/joernih/sfb10816mikrooekonomi/blob/main/inst/forelesningsnotater/pdfs/6_produsent_prodm_arbm.pdf)

## Konsumentteori: Konsumentens økonomiske adferd

Forelesning #5: [`r tema[5]`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/pdfs/7_konsumentens_tilpasning.pdf)

Forelesning #6: [`r tema[6]`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/pdfs/8_gode_og_arbeidsmarked.pdf))

## Markedsteori

Forelesning #7: [`r tema[7]`](https://github.com/joernih/sfb10816mikrooekonomi/blob/main/inst/forelesningsnotater/pdfs/9_markedsteori_fk.pdf)

Forelesning #8: [`r tema[8]`](https://github.com/joernih/sfb10816mikrooekonomi/blob/main/inst/forelesningsnotater/pdfs/10_markedsteori_mp.pdf)

Forelesning #9: [`r tema[9]`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/pdfs/11_markedsteori_uk.pdf)

Forelesning #10  [`r substring(tema[10],1,43)`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/pdfs/12_prisdiskriminering.pdf)

## Andre Emner

Forelesning #10 [`r substring(tema[10],45)`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/pdfs/14_18_andre_emner.pdf)

Forelesning #11  [`r tema[11]`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/pdfs/13_effektivitet_markedssvikt.pdf)

Forelesning #12 [`r substring(tema[12],0,20)`](https://github.com/joernih/SFB10816Mikrooekonomi/blob/main/inst/forelesningsnotater/pdfs/15_tilpasning_tid.pdf)

```{r echo=F}
knitr::knit_exit()
```



