---
title: "Images"
#subtitle: "Forelesningsnotater (shift+o for oversiksbilde)"
author: "Jørn I. Halvorsen og Joachim Thøgersen"
date: "2021/08/12 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    includes:
      in_header: "mathjax-equation-numbers.html"
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      count:IncrementalSlides: false
#output:
#  html_document:
#    toc: true
#    theme: united
---

```{r xaringan-tile-view, echo=FALSE, message=F, warning=F}
xaringanExtra::use_editable(expires = 1)
xaringanExtra::use_tile_view()
#xaringanExtra::use_share_again()
xaringanExtra::use_scribble()
xaringanExtra::use_webcam()
#xaringanExtra::use_slide_tone()
xaringanExtra::use_panelset()
library(htmlTable)
library(magrittr)
library(xaringan)
library(plotly)
```

```{r eval=FALSE, include=FALSE}
#- Eksempel med $U(x_1, x_2) = 10x_1x_2$
pathn <- '/inst/forelesningsnotater/abc'
xaringan::inf_mr(paste0(rprojroot::find_rstudio_root_file(),pathn,'.Rmd'))
system(paste0('brave ',rprojroot::find_rstudio_root_file(),pathn,'.html'))
servr::daemon_stop()
rmarkdown::render(paste0(rprojroot::find_rstudio_root_file(),pathn,'.html'))
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
source(paste0(rprojroot::find_rstudio_root_file(),'/inst/forelesningsnotater/timeplan.R'))
```

---

# First

Different image formats in Linux have different properties that determine how they are used and the applications they are best suited for. Here is a brief description of some of the most common image formats in Linux:

JPEG/JPG: JPEG (Joint Photographic Experts Group) is a widely-used image format that supports lossy compression. JPEG images are compressed to reduce file size, which can lead to some loss of image quality. This format is best suited for photographs and other complex images with a wide range of colors.

PNG: PNG (Portable Network Graphics) is a lossless image format that supports transparency. PNG images are not compressed as much as JPEGs, so they tend to have larger file sizes, but they retain more of the original image quality. This format is best suited for images that require transparency, such as logos and icons.

---

# Second

GIF: GIF (Graphics Interchange Format) is a lossless image format that supports animations. GIFs are limited to 256 colors, so they are not ideal for complex images or photographs, but they are commonly used for simple animations and short video clips.

BMP: BMP (Bitmap) is a simple image format that supports uncompressed color data. BMP images are not compressed, which means they can have very large file sizes, but they are compatible with many different software applications and platforms.

TIFF: TIFF (Tagged Image File Format) is a flexible image format that supports lossless compression and can be used for both grayscale and color images. TIFF images can be quite large, but they are commonly used in professional settings for high-quality printing and document archiving.

---

# Third

SVG: SVG (Scalable Vector Graphics) is a vector-based image format that is scalable to any size without losing image quality. SVG images are typically used for logos, icons, and other graphics that need to be resized frequently without losing clarity or detail.

These are just a few examples of the most common image formats in Linux, and there are many other formats available with different properties and uses.

```{r}
knitr::knit_exit()
```

---


